Layered Formal Verification of a TCP Stack

### 2021-06-03 SecDev21/paper.tex
Minor additions

In total, for this work, 50 subprograms have been translated from C to SPARK. This accounts for 2266 lines of code, of which 1165 are SPARK logic code (e.g.\ contracts) used to represent and prove TCP specification. The overall proving time with GNATprove is 10 minutes on a 12-processor Intel(R) Core(TM) i7-9750H CPU with 2.60GHz speed and 16GB of RAM.

>>>>

In total, for this work, 50 subprograms have been translated from C to SPARK. This accounts for 2266 lines of code, of which 1165 are SPARK logic code (e.g.\ contracts) used to represent and prove TCP specification. The overall proving time with GNATprove from the Community 2021 release is 10 minutes on a 12-processor Intel(R) Core(TM) i7-9750H CPU with 2.60GHz speed and 16GB of RAM. The tools and code are freely available online.
